%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Full-Time Experience}
\begin{cventries}

%---------------------------------------------------------
  \cvopenentry
   {Software Engineer} % Job title
    {Apple} % Organization
    {Cupertino, CA} % Location
    {\textbf{1+ Year} | July 2023 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Integrated on device LLM Machine Learning frameworks and built interfaces to deliver intelligent features on Safari iOS app.}
        \item {Key contributor to DMA-related projects, ensuring user privacy and regulative compliance while preserving performance.}
        \item {Developing and optimizing Safari and Webkit browser components and features on iOS using C++, Objective-C and Swift.}
        %\item {Collaborated with cross-functional teams to enhance web rendering performance, reduce app load times, and improve UX.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cvopenentry
   {Full Stack Software Developer} % Job title
    {\href{https://vagon.io}{Vagon}} % Organization
    {Remote} % Location
    {\textbf{2 Years} | Mar 2020 - Jan 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        %\item {Superved and lead to Front End team to develop fast and reliable remote desktop controller application on web.} 
        \item {Maintained and optimized full-stack applications, leveraging React, Ruby on Rails, Postgre SQL, AWS, Docker.}
	\item {Enhanced live streaming service performance 30\% using WebRTC and WebSocket connection and browser decoder APIs.}
	\item {Reduced monthly fraud cases 80\% by implementing improved payment systems with fraud detection, prevention methods.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cvopenentry
   {Open Source Contributor} % Job title
    {\href{https://www.mozilla.org}{Mozilla / Firefox Devtools}} % Organization
    {Remote} % Location
    {\textbf{3 Months} | Jan 2020 - Mar 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Identified and fixed bugs on Github and Bugzilla(Phabricator) under Firefox projects, mainly on Firefox Devtools.}
        %\item {Created previewer that shows the visual content of the website in the timeline for performance recording tool Firefox Profiler}
        \item {Reworked Firefox reader mode design and integrated reader-specific buttons to work with browser settings.}
      \end{cvitems}
    }
\end{cventries}
\cvsection{Internship Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cvopenentry
   {Software Engineering Intern} % Job title
    {Google} % Organization
    {San Francisco, CA} % Location
    {\textbf{4 Months} | Aug 2022 - Nov 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a tool to track and identify latency changes in Google Cloud products and diagnose potential bottlenecks.}
        \item {Implemented a TypeScript dashboard and Go back-end to aggregate billions of logs using SQL queries and visualize data.}
        \item {Created documents to prepare team for migrating to more modern internal frameworks and organized workshops.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cvopenentry
   {Software Engineering Intern} % Job title
    {Apple} % Organization
    {Cupertino, CA} % Location
    {\textbf{4 Months} | May 2022 - Aug 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented key features in an in-house recommendation and prediction system, improving predictive accuracy for incomplete search inputs by 4\%.}
        \item {Collaborated with Safari and Webkit team members to enhance the functionality and reliability of the search system.}
        \item {Resolved critical Safari bugs using Objective-C, contributing to a smoother user experience and reduced crash rates.}
        %\item {Designed, proposed, and implemented features for the next major release that more than 1 billion users will use.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cvopenentry
   {Software Developer Intern} % Job title
    {\href{https://zeplin.io}{Zeplin}} % Organization
    {San Francisco,CA} % Location
    {\textbf{3 Months} |Jun. 2019 - Aug. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on React Web and Electron Windows applications and developed components that are used across all application.}
		\item {Migrated Profile Pages(Account settings, Billing, Subscriptions) to React from vanilla Javascript, HTML, CSS.}
        \item {Reduced code redundancy around 30\% in Profile Pages and increased loading speed around 10\%. }
      \end{cvitems}
    }
    %{./images/zeplin}
%---------------------------------------------------------
%   \cvopenentry
%    {Software Developer Intern} % Job title
%     {Alibaba Group / Trendyol.com} % Organization
%     {Istanbul, Turkey} % Location
%     {Jul. 2018 - Dec. 2018} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
% %        \item {Working on the back-end side of Marketplace project.}
% 		 \item {Developed web services for seller interface of e-commerce application using Java Spring Boot, REST API, RabbitMQ.}
%         \item {Implemented new microservice features to Seller Portal that are used for adding and tracking products in marketplace.}
% %        \item {Using agile software, pair programming and test driven development methods.}
%       \end{cvitems}
%     }
%     %{./images/trendyol}
%---------------------------------------------------------


\begin{comment}
  \cvopenentry
   {Full-Stack Software Developer
   } % Job title
    {Vagon.io} % Organization
    {Remote} % Location
    {Mar. 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Supervising and leading to Front End team to develop fast and reliable remote desktop controller application on web}
        \item {Working on Web and back-end applications using React, Ruby on Rails, PostgreSQL, AWS, Docker.}
        \item {Built a module that installs software on machine images and distributes them to 8 cloud regions.}
		\item {Improved live streaming service performance by 30\% using Websocket connection and browser decoder APIs.}
		\item {Increased fraud detection, prevention methods and changed payment systems. Monthly fraud cases decreased by 80\%.}
      \end{cvitems}
    }
    %{./images/vagon}
\\
%---------------------------------------------------------
  \cvopenentry
   {Open Source Contributor} % Job title
    {Mozilla / Firefox Devtools} % Organization
    {Remote} % Location
    {Jan.2020 - Mar. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on Firefox projects, mainly on Firefox Devtools. Solved and reported issues on Github and Bugzilla(Phabricator).}
        \item {Created previewer that shows the visual content of website in timeline for performance recording tool Firefox Profiler.
        \item {Reworked Firefox reader mode design and integrated reader specific buttons to work with browser settings.}
}
      \end{cvitems}
    }
    %{./images/mozilla}
    
  \cvopenentry
   {Software Developer Intern} % Job title
    {Trendyol.com} % Organization
    {Istanbul, Turkey} % Location
    {July. 2018 - Dec. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item {Working on the back-end side of Marketplace project.}
		\item {Developing web services using REST API, Java Spring Boot, RabbitMQ .}
        \item {Implementing new features and microservices to Supplier and Admin Portal.}
%        \item {Using agile software, pair programming and test driven development methods.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cvopenentry
    {Work \& Study} % Job title
    {Koc University, Computer Information Technology Department} % Organization
    {Istanbul, Turkey} % Location
    {OCt. 2015 - May. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Applied and tested Google Cloud technologies across the campus.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{comment}
\end{cventries}
