%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Leadership \& Volunteer Experience}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cvopenentry
    {University Innovation Fellow} % Affiliation/role
    {Stanford University Hasso Plattner Institute of Design (d.school) } % Organization/group
    {} % Location
    {Oct. 2019 - 2021} % Date(s)
    {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Completed a 7-week-long design thinking and innovation course, brainstormed and launched new ideas.}
        \item {Planned and piloted an orientation program with faculty to enhance new students' understanding of university resources.}
        %\item {Nominated and gained scholarship by Koc University Office of International Programs} to become a fellow.
        %\item {Created an orientation program with faculty that aims to give new students a better overview of university.}
        %\item {\textbf{Cofounded} a team which achieved to make an impact and open a \textbf{Makerspace} in campus.}
     \end{cvitems}
    }
%---------------------------------------------------------
  \cvopenentry
    {Cofounder of Koc University Makerspace Lab} % Affiliation/role
    {Global Learning and Leadership Program} % Organization/group
    {} % Location
    {Sept. 2016 - 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        %\item {\textbf{Cofounder} of a team which achieved to make an impact and open a Makerspace in campus.}
        \item {Secured funding from the engineering faculty to design and equip the Makerspace, after a one-year pivot project.}
        \item {Led a team of 15 members, organizing workshops on computer science, and creative skills for over 200 participants.}
        \item {By Spring 2019, the Makerspace supported 40\% of all senior engineering projects as a student-led innovation hub.}
%       \item {Managing the team members and coordinating them.}
%        \item {Giving technical advices to students who have projects and helping them to prototype their ideas.}
     \end{cvitems}
    }
%---------------------------------------------------------
  \cvopenentry
    {Global Volunteer} % Affiliation/role
    {AIESEC Cairo, Egypt} % Organization/group
    {} % Location
    {Summer 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        %\item {Was a member of an international team of 30 people which was responsible from building a school from throw-out materials such as plastic bottles, car tires in a poor island in Nile, Egypt. }
        \item {Collaborated with an international team of 30 to construct a school using recycled materials %such as plastic bottles and car tires on a 
        disadvantaged Nile island.}
      \end{cvitems}
    }

%---------------------------------------------------------

\begin{comment}
Commented code
%---------------------------------------------------------
  \cventry
    {Reviewer and Participant} % Affiliation/role
    {Algorithm Competition Programme} % Organization/group
    {Inzva, Istanbul} % Location
    {Oct. 2018 - May. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Participated in the 30-week Algorithm Competition Programme which includes lectures, contests, and a variety of practises.}
      \end{cvitems}
    }
    \vspace{2mm}
\cventry
    {Member} % Affiliation/role
    {Association for Computing Machinery Society} % Organization/group
    {Koc Universtiy} % Location
    {Oct. 2017 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Responsible for organizing IoT and robotics related workshops, conferences for new members. }
        \item {Developing tech-projects to attend national and international competitions. }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Global Volunteer in Egypt } % Affiliation/role
    {AIESEC} % Organization/group
    {Cairo, Egypt} % Location
    {Summer 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Was a member of an international team of 30 people which was responsible from building a school from throw-out materials such as plastic bottles, car tires on an impoverished island in the Nile, Egypt.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{comment}
\end{cventries}
