%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Advanced Course Projects}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------

  \cvopenentry
   {Eye Disease Classification System} % Job title
    {Senior Design Project | fundeus.xyz} % Organization
    {} % Location
    {Oct. 2020 - Jan. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Implemented Machine Learning algorithms that can classify cataract, glaucoma, and diabetic retinopathy from fundus images.}
      	\item {Designed the overall scalable cloud system and prepared front-end, back-end applications of the project using React, Ruby, and AWS.}
        \item {Selected as one of the best projects of the year and awarded with the outstanding grade of A+ for our work.}
      \end{cvitems}
    }
%\cventry
%   {TCP Layer Protocol Design} % Job title
%    {Computer Networks Project} % Organization\input{cv/projects.tex}
%    {} % Location
%    {Oct. 2020 - Present} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%      	\item {Build server and client systems that use designed messaging protocol over TCP.}
%      	\item {Designed flexible and secure protocol...  }
%      \end{cvitems}
%    }
\cvopenentry
   {Review Paper: YCSB vs BigBench} % Job title
    {Internet-scale Distributed Systems} % Organization
    {} % Location
    {Apr. 2020 - Aug. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Prepared and presented a paper that compares Yahoo! Cloud Serving Benchmark(YCSB) and         BigBench Benchmark tools.}
      	\item {Read and discussed a total of 30 papers about recent Distributed Systems Technologies during the semester.}
      \end{cvitems}
    }
\cvopenentry
   {Cardiac Electrophysiology Simulator} % Job title
    {Parallel Programming Course Project} % Organization
    {} % Location
    {Jan. 2019 - Jun. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Implemented 3 versions of a serial cardiac electrophysiology simulator using MPI, OpenMP, and Nvidia CUDA.}
      	\item {Optimized multi-core GPU performances of MPI, OpenMP, and Nvidia CUDA versions and prepared performance comparison report on different input scales.}
      \end{cvitems}
    }
\cvopenentry
   {Multithreaded Game with Network} % Job title
    {Software Engineering Course Project} % Organization
    {} % Location
    {Oct. 2018 - Jan. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Developed an online game based on Ultimate Monopoly board game with a team of 5 people and acted as a team leader.} 
      	\item {Designed the network and thread related parts of the project and applied GoF design patterns.} 
      	\item {Selected as the best project among 20 other projects by the professor and TAs.} 
      \end{cvitems}
    }

\end{cventries}
