%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
%\vspace{\acvSectionRemove}
\cvsection{Research \& Teaching Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
 %---------------------------------------------------------
  \cventry
    {Advisor: Prof. Öznur Özkasap} % Affiliation/role
    {Koc University} % Organization/group
    {Istanbul, Turkey} % Location
    {Jan. 2019 - Jun. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Worked on Skip Graph simulator project in Network and Distributed Systems Laboratory.}
        \item {Developed Java implementations and test cases for node search and availability algorithms.}
      \end{cvitems}
    }
%---------------------------------------------------------

  \cventry
    {Teaching Assistant } % Affiliation/role
    {Stanford – Koc University CS Bridge Program} % Organization/group
    {} % Location
    {Summer 2017-Summer 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Was section leader of a Java teaching program directed by Nick McKeown who has taught computer science at Stanford.}
        \item {Was responsible for preparing and grading assignments, conducting problem solving sections, helping students during lab-hours and giving feedbacks to daily assignments.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Advisor: Prof. M. Cengiz Onbasli} % Affiliation/role
    {Koc University} % Organization/group
    {Istanbul, Turkey} % Location
    {Oct. 2017 - May. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Built and deployed overall Internet of Things(IoT) project with Raspberry pi, camera, temperature and weight sensors.  }
        \item {Developed native mobile application for Android. }
       	\item {Used machine learning algorithm for food recognition and several AWS stack including Rekognition, S3, Dynamodb, Lambda.} 
        \item {Conducted penetration testing commissioned by national agency and corporation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Advisor: Prof. Oguz Turan Buruk} % Job title
    {Koc University, Arcelik Research Center for Creative Industries} % Organization
    {Istanbul, Turkey} % Location
    {Oct. 2016 - Oct. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
%       	\item {Worked on an Internet of Things(IoT) project which was proposed by me and funded by Arcelik.}
         \item {Worked on a research about applications  of wearable technologies in gamification and prototyped a hand controller with Arduino and 3D Printing.}
      \end{cvitems}
    }
%---------------------------------------------------------

%---------------------------------------------------------
\end{cventries}
