%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
\vspace{-1mm}
%---------------------------------------------------------
  \cvexpentry
   {Software Engineering Intern} % Job title
    {Google} % Organization
    {San Francisco, CA} % Location
    {\textbf{3 Months} | Aug 2022 - Nov 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a tool to track and identify latency changes in Google Cloud products and diagnose potential causes.}
        \item {implemented a TypeScript dashboard and Go back-end to aggregate billions of logs using SQL queries and visualize data.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cvexpentry
   {Software Engineering Intern} % Job title
    {Apple} % Organization
    {Cupertino, CA} % Location
    {\textbf{3 Months} | May 2022 - Aug 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked as a member of \textbf{Safari iOS} team. Solved \textbf{Safari macOS} and \textbf{WebKit} bugs using \textbf{Objective-C}. }
        \item {Proposed and implemented new features for the upcoming major release of Safari, for a user base of over \textbf{1 billion} people.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cvexpentry
   {Full Stack Software Developer} % Job title
    {\href{https://vagon.io}{Vagon.io}} % Organization
    {Remote} % Location
    {\textbf{18 Months} | Mar 2020 - Jan 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        %\item {Superved and lead to Front End team to develop fast and reliable remote desktop controller application on web.} 
        \item {Maintained Web and back-end applications using \textbf{ React JavaScript, Ruby on Rails, Postgre SQL, AWS, Docker}.}
	\item {Enhanced live streaming service performance \textbf{30\%} using WebSocket connection and browser decoder APIs.}
	\item {Slashed monthly fraud cases \textbf{80\%} by implementing improved payment systems with fraud detection, prevention methods.}
      \end{cvitems}
    }
    %{./images/vagon}
%---------------------------------------------------------
  \cvexpentry
   {Open Source Contributor} % Job title
    {\href{https://www.mozilla.org}{Mozilla / Firefox Devtools}} % Organization
    {Remote} % Location
    {\textbf{3 Months} | Jan 2020 - Mar 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Identified and fixed bugs on \textbf{Github} and \textbf{Bugzilla(Phabricator)} under \textbf{Firefox} projects, mainly on \textbf{Firefox Devtools}.}
        %\item {Created previewer that shows the visual content of the website in the timeline for performance recording tool Firefox Profiler}
        \item {Reworked Firefox reader mode design and integrated reader-specific buttons to work with browser settings.}
      \end{cvitems}
    }
    %{./images/mozilla}
%---------------------------------------------------------
  \cvexpentry
   {Software Developer Intern} % Job title
    {\href{https://zeplin.io}{Zeplin.io (Y Combinator Start-up)}} % Organization
    {San Francisco,CA \& Istanbul} % Location
    {\textbf{3 Months} | Jun 2019 - Aug 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed \textbf{React front-end and Electron} applications and developed components that are used across all applications.}
	%\item {Migrated Profile Pages(Account settings, Billing, Subscriptions) \textbf{to React JS} from vanilla \textbf{Javascript, HTML, CSS}}
        \item {Redesigned and reduced code redundancy and increased loading speed by around \textbf{30\%} and\textbf{10\%}, respectively, in Profile Pages.}
      \end{cvitems}
    }
    %{./images/zeplin}
%---------------------------------------------------------
  \cvexpentry
   {Software Engineering Intern} % Job title
    {Trendyol.com (Alibaba Group)} % Organization
    {Istanbul, Turkey} % Location
    {\textbf{5 Months} | Jul 2018 - Dec 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item {Working on the back-end side of Marketplace project.}
		 \item {Developed web services for seller interface of e-commerce application using \textbf{Java Spring Boot, REST API, Kubernetes}.}
        %\item {Built and tested new microservice features to Seller Portal that are used for adding and tracking products in marketplace}
%        \item {Using agile software, pair programming and test driven development methods.}
      \end{cvitems}
    }
    %{./images/trendyol}
\begin{comment}
%---------------------------------------------------------
  \cvexpentry
   {Software Engineering Intern} % Job title
    {Trendyol.com (Alibaba Group)} % Organization
    {Istanbul, Turkey} % Location
    {\textbf{5 Months} | Jul 2018 - Dec 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item {Working on the back-end side of Marketplace project.}
		 \item {Developed web services for seller interface of e-commerce application using \textbf{Java Spring Boot, REST API, Kubernetes}.}
        %\item {Built and tested new microservice features to Seller Portal that are used for adding and tracking products in marketplace}
%        \item {Using agile software, pair programming and test driven development methods.}
      \end{cvitems}
    }
    %{./images/trendyol}
%---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {Koc University, Arcelik Research Center for Creative Industries} % Organization
    {Istanbul, Turkey} % Location
    {\textbf{1+ Years} | Oct 2016 - Feb 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
%       	\item {Worked on an Internet of Things(IoT) project which was proposed by me and funded by Arcelik.}
       	\item {Built overall Internet of Things(IoT) project with Raspberry Pi\&sensors and developed Android Application}
        %\item {Developed native mobile application for Android. }
       	\item {Used machine learning algorithm for food recognition and several AWS stack including Rekognition, S3, Dynamodb, Lambda.} 
         %\item {Worked on a research about applications of wearable technologies and prototyped the project with %Arduino and 3D Printing.  }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Work \& Study} % Job title
    {Koc University, Computer Information Technology Department} % Organization
    {Istanbul, Turkey} % Location
    {OCt. 2015 - May. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Applied and tested Google Cloud technologies across the campus.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
  {Web Application}
  {Personal Project - ku-bookshare.github.io} % Job title
     % Organization
    {} % Location
    {3+ Months | Mar. 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Developing React web application which users can donate or borrow books from the shelves among KU campus. } 
      \end{cvitems}
    }

%---------------------------------------------------------
\end{comment}
\end{cventries}
