%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cvopenentry
    {University Innovation Fellow} % Affiliation/role
    {Stanford d.school | University Innovation Fellows (UIF)} % Organization/group
    {Stanford University, California} % Location
    {Oct 2019 - Present} % Date(s)
    {
    \begin{cvopenitems} % Description(s) of experience/contributions/knowledge
        %\item {Nominated and gained scholarship by Koc University Office of International Programs} to become a fellow.
        \item {Concluded a 7 week-long design thinking, and innovation online education, brainstormed and launched new ideas}
        \item {Planned and piloted an orientation program with faculty that aims to give new student a better overview of university}
        %\item {\textbf{Cofounded} a team which achieved to make an impact and open a \textbf{Makerspace} in campus.}
     \end{cvopenitems}
    }
%---------------------------------------------------------
  \cvopenentry
    {Teaching Assistant } % Affiliation/role
    {Stanford – Koc University CS Bridge Program} % Organization/group
    {} % Location
    {Summer 2017-Summer 2018} % Date(s)
    {
      \begin{cvopenitems} % Description(s) of experience/contributions/knowledge
        \item {Was \textbf{section leader} of a \textbf{Java teaching} program directed by Nick McKeown who has taught CS at Stanford for 20 years}
        \item {Prepared and graded assignments, coordinated problem solving sections}
      \end{cvopenitems}
    }
%---------------------------------------------------------

\begin{comment}
Commented code
%---------------------------------------------------------
  \cventry
    {Cofounder of Koc University Makerspace Lab} % Affiliation/role
    {Global Learning and Leadership Program} % Organization/group
    {Koc Universtiy} % Location
    {Sept. 2016 - Nov. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        %\item {\textbf{Cofounder} of a team which achieved to make an impact and open a Makerspace in campus.}
        \item {Funded by engineering faculty to design the space and chose the required tools after one year of pivot project.}
        \item {Coordinated team members and arranged workshops about computer science, creative skills, and social innovation.}
        \item {In Spring 2019, \textbf{40\%} of all senior engineering projects developed in fully student driven Makerspace.}
%       \item {Managing the team members and coordinating them.}
%        \item {Giving technical advices to students who have projects and helping them to prototype their ideas.}
     \end{cvitems}
    }
    \vspace{2mm}
%---------------------------------------------------------
  \cventry
    {Reviewer and Participant} % Affiliation/role
    {Algorithm Competition Programme} % Organization/group
    {Inzva, Istanbul} % Location
    {Oct. 2018 - May. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Participated in the 30-week Algorithm Competition Programme which includes lectures, contests, and a variety of practises.}
      \end{cvitems}
    }
    \vspace{2mm}
\cventry
    {Member} % Affiliation/role
    {Association for Computing Machinery Society} % Organization/group
    {Koc Universtiy} % Location
    {Oct. 2017 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Responsible for organizing IoT and robotics related workshops, conferences for new members. }
        \item {Developing tech-projects to attend national and international competitions. }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Global Volunteer in Egypt } % Affiliation/role
    {AIESEC} % Organization/group
    {Cairo, Egypt} % Location
    {Summer 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Was a member of an international team of 30 people which was responsible from building a school from throw-out materials in a poor island in Egypt. }
      \end{cvitems}
    }

%---------------------------------------------------------
\end{comment}
\end{cventries}
